### 2012-03-21 htdocs/user.tex
BPIII initialisation added
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@1544 40876441-3496-0410-a613-a2fca35b2ae2

There are a number of useful choices here. The key value
\texttt{twist} initialises a simple cholesteric with the
helical axis in the $z-$direction;  \texttt{o8m}
gives equilibrium BPI, \texttt{o2} gives BPII. The appropriate
choices for the other parameters must be made correspondingly.

@@

The constraint in this case is that $2a_h + h_c < L_{local}$, ie.,
there is effectively one cell in each local domain. This option
should not be required in normal circumstances.

@@

>>>>

There are a number of useful choices here. The key value
\texttt{twist} initialises a simple cholesteric with the
helical axis in the $z-$direction, whereas the values 
\texttt{cholesteric\_x\_y\_z} provide according initialisations 
with twist along the other axes.
The value \texttt{o8m} gives equilibrium BPI, \texttt{o2} gives BPII.
Another, cubic body-centered BP is obtained by the value \texttt{o5}.
Hexagonal BPs are initialised with \texttt{h2d, h3da} and \texttt{h3db}.\\
BPIII emerges from randomly positioned and oriented DTCs 
embedded into an isotropic or cholesteric environment.
It is initialised with the key value \texttt{bp3}, whereas the number
$N$ and radius $R$ of the DTCs and the type of the environment 
$ENV=\{0,1\}$, (0 = isotropic, 1 = cholesteric), is specified with the key value
\texttt{lc\_init\_bp3} $N\_R\_ENV$.\\
The appropriate choices for the other parameters must be made correspondingly.

@@

The constraint in this case is that $2a_h + h_c < L_{local}$, ie.,
there is effectively one cell in each local domain. (In practice,
the constraint is slightly tighter than this if larger halo regions
are in effect.) This option
should not be required in normal circumstances.

@@

\subsubsection{Flat wall lubrication correction}

It is possible to prevent colloids colliding with the flat boundary walls
by adding the correction to the normal component of the lubrication
force. The general form of this correction is
\begin{equation}
\mathbf{F}_{\mathrm{lub}} = -6\pi \eta a_h^2
%({\textstyle \frac{1}{h} - \frac{1}{h_c}})
(1/h - 1/h_c)
\mathbf{u} . \mathbf{r}.
\end{equation}
Here, $h$ is the surface to surface separation, and $h_c$ is the cutoff
distance beyond which the correction is not applied. The relative
velocity (assuming the wall is not moving) and normal separation are
$\mathbf{u}$ and $\mathbf{r}$ respectively.

The cutoff distance can be set from the input via

\inputkey{boundary\_lubrication\_rcnormal 0.1}

where the value is (strictly) set via calibration, cf. the hydrodynamic
radius. In general, the cutoff is between zero and 0.5 lattice spacing,
and can be smaller for larger particles. Because the wall velocity is
fixed, this force correction should cause no stability issues in the
colloid velocity update (provided a colloid's initial position is not
very close to the wall). By default the cutoff $h_c = 0$.
